The Transition from Massive Metal Free Stars to Dwarf Galaxies

### 2011-03-13 ms.tex
Removing no H2 cooling run (leave it for a separate paper).  Removing halo mass function.

We perform ten different simulations with the same initial conditions.
The baseline model considers (a) primordial cooling with 9 species of
hydrogen, helium, and molecular hydrogen, (b) a Pop III IMF
characteristic mass $M_{\rm char}$ = 100 \Ms, (c) Pop II and Pop III
star formation, and (d) a critical metallicity of [Z/H] = --4.  We
vary this model with the following changes:

\begin{enumerate}
\item Additional radiative cooling from metal lines.  We calculate a
  cooling curve with CLOUDY \citep{CLOUDY} and use the method of
  \citep{2008MNRAS.385.1443S}.  Solar abundances were used in the
  cooling curve.  It is tabulated based on density, temperature,
  electron fraction, and total metallicity.
\item A critical metallicity of [Z/H] = --5 and --6, accounting for
  the case where dust cooling can induce low-mass fragmentation in
  these lower metallicities \citep{Omukai05, Schneider06_Frag}.
\item Higher Pop II metal yield of $y = 0.025$ that is consistent with
  average values in the Milky Way \citep{Madau96}.
\item Pop III IMF characteristic mass $M_{\rm char}$ = 40 \Ms.  Using
  the abundance patterns of EMP stars and reionization as constaints,
  the data are best fit with IMFs favoring stars with masses between
  20--130 \Ms~\citep{Umeda03, Tumlinson06}.
\item Lyman-Werner radiation background.  We use the semi-analytical
  model of \citet{Wise05}, updated with the 7-year WMAP parameters and
  optical depth to Thompson scattering, to calculate the LW background
  intensity, plotted in Fig. \ref{fig:uvb}.  In this semi-analytical
  model, we use a Pop III stellar mass of 100 \Ms, star formation
  efficiency of 0.005, and escape fraction of 0.2 \citep{Wise09}.  The
  LW radiation from point sources are added to the background.  The
  intensity decreases after $z \sim 14$ because Pop II star formation
  becomes dominant, which produce less LW specific luminosity than Pop
  III stars that have surface temperatures of $T = 10^5$ K.  For
  computational convenience, we fit the background evolution with the
  function
%
  \begin{equation}
    \label{eqn:uvb}
    \log_{10} J_{21}(z) = A + Bz + Cz^2 + Dz^3 + Ez^4,
  \end{equation}
%
  where $(A,B,C,D,E) = (-2.356, 0.4562, -0.02680, 5.882 \times 10^{-4},
  -5.056 \times 10^{-6})$ and $J_{21}$ is the specific intensity in
  units of $10^{-21}$ \emis.  This fits the
  model data within 1\% in $6 \le z \le 30$ and is consistent with
  $J_{21}$ values in \citet{Trenti09_SFR}.
\item Pop II star formation only.  This model is useful to study the
  importance of treating Pop III star formation as single stars and
  their pair-instability and Type II SNe.
\item Pop II star formation only and no molecular hydrogen cooling.
  This model provides a good comparison to larger scale simulations
  where it is not computationally feasible to consider \hh~cooling or
  resolve the necessary scales for Pop III star formation.
\item Combination of metal cooling (model i), increased metal yields
  (model iii), a LW background (model v).  This provides the best
  physical scenario for the high-$z$ universe, and we consider it as
  our \textit{primary model}.
\end{enumerate}

@@

\begin{figure}
  \plotone{mass_fn.eps}
  \caption{\label{fig:mass_fn} Halo DM mass function of the simulated
    haloes (points) where the error bars are Poisson noise and the
    solid line is the analytic halo mass function of
    \citet{Warren06}.}
\end{figure}

@@

Here we present the gaseous and stellar evolution of the high-redshift
dwarf galaxies that form in our \textit{primary physical model} with
metal-line radiative cooling, Pop II metal yields that agree with MW
data, and a LW radiation background.  To illustrate its global
properties, we show the density-weighted projections of gas density,
temperature, and metallicity at redshifts 15, 12, 10, 8, and 7 in
Fig. \ref{fig:evo-mosaic}.  Most apparent is the photo-heating of IGM
over this redshift range, where the mass- and volume-averaged ionized
fraction are 0.431 and 0.417 at $z=7$, respectively.  The metallicity
projections show the growth of metal-enriched bubbles, starting first
with enrichment from Pop III stars.  Then as time progresses, the
haloes enriched within these bubbles above $Z_{\rm cr}$ transition to
Pop II star formation, enriching their host halo and surrounding IGM.
In Fig. \ref{fig:mass_fn}, we show the halo mass function, agreeing
well with the analytic halo mass function of \citet{Warren06}.  We
identify the haloes with a friends-of-friends (FOF) algorithm
\citep{Davis85}.  The excess of low-mass haloes below $M_{\rm DM} = 2
\times 10^6 \Ms$ is most likely associated with the biased region in
the lower-right region in the projections.  Furthermore, the
uncertainities in different analytic halo mass functions
\citep[see][for a comparison]{Reed07} and halo identification are
comparable than these differences.  Our fidicual model contains 38
galaxies with a total of 3640 Pop II star clusters and captures the
formation of 333 Pop III stars.

@@

\begin{figure*}
  \plottwo{z7-mosaic0.eps}{z7-mosaic1.eps}
  \caption{\label{fig:z7-mosaic} Density-weighted projections of
    density (left), temperature (center), and metallicity (right) of
    the 10 most massive haloes at $z=7$.  The field of view is 5 proper
    kpc, and the circles have a radius of $r_{200}$.  The composite
    metallicity images are constructed in the same fashion as
    Fig. \ref{fig:evo-mosaic}.}
\end{figure*}

\begin{figure*}
  \plottwo{z8-mosaic0.eps}{z8-mosaic1.eps}
  \caption{\label{fig:z8-mosaic} Same as Fig. \ref{fig:z7-mosaic} but
    at $z=8$, showing the progenitors of the 10 most massive haloes at
    $z=7$.}
\end{figure*}

\begin{figure*}
  \plottwo{z10-mosaic0.eps}{z10-mosaic1.eps}
  \caption{\label{fig:z10-mosaic} Same as Fig. \ref{fig:z8-mosaic} at
    $z=10$.}
\end{figure*}

To get a visual sense of the mass accretion and metal enrichment
history of the 10 most massive haloes, we show their density-weighted
projections of gas density, temperature, and composite Pop II+III
metallicity at redshifts 7, 8, and 10 in
Fig. \ref{fig:z7-mosaic}--\ref{fig:z10-mosaic}, respectively.  One
common feature of all of the halos represented in these Figures is
that they are embedded in a preheated IGM with the exception of Halo 7
at $z=10$.  Prior radiative feedback in either the host or nearby
halos created \hii~regions that encompass these halos.  For
\hii~regions without sustained star formation, these so-called relic
\hii~regions recombine and radiatively cool down to $T = 10^3$ K.
Within the virial radius, one can see that our simulations capture the
multi-phase ISM.  In the density projections, the effects of
photo-evaporation and cloud crushing are clearly seen, which are
caused by the stellar radiative and mechanical feedback, respectively.
The filaments adjacent to the halos are photo-heated to $T = 1-3
\times 10^4$ K, and then their gas escapes into the IGM no longer
being pressure equilibrium with the gravitational potential of the
filament, i.e. Jeans smoothing.  Furthermore, neighboring halos are
photo-evaporated \citep[see][for the level of halo
  photo-evaporation]{Wise08_Reion}, resulting in the suppression of
gas-rich satellite haloes.  A good illustration of photo-evaporation
in progress is the cometary structure in the bottom-center of the
density projection of Halo 4 at $z=7$.

@@

\section{Differences between Physical Models}
\label{sec:models}

@@

\subsection{Neglecting Pop III star formation and \hh~formation}

>>>>

We perform nine different simulations with the same initial conditions.
The baseline model considers (a) primordial cooling with 9 species of
hydrogen, helium, and molecular hydrogen, (b) a Pop III IMF
characteristic mass $M_{\rm char}$ = 100 \Ms, (c) Pop II and Pop III
star formation, and (d) a critical metallicity of [Z/H] = --4.  We
vary this model with the following changes:

\begin{enumerate}
\item Additional radiative cooling from metal lines.  We calculate a
  cooling curve with CLOUDY \citep{CLOUDY} and use the method of
  \citep{2008MNRAS.385.1443S}.  Solar abundances were used in the
  cooling curve.  It is tabulated based on density, temperature,
  electron fraction, and total metallicity.
\item A critical metallicity of [Z/H] = --5 and --6, accounting for
  the case where dust cooling can induce low-mass fragmentation in
  these lower metallicities \citep{Omukai05, Schneider06_Frag}.
\item Higher Pop II metal yield of $y = 0.025$ that is consistent with
  average values in the Milky Way \citep{Madau96}.
\item Pop III IMF characteristic mass $M_{\rm char}$ = 40 \Ms.  Using
  the abundance patterns of EMP stars and reionization as constaints,
  the data are best fit with IMFs favoring stars with masses between
  20--130 \Ms~\citep{Umeda03, Tumlinson06}.
\item Lyman-Werner radiation background.  We use the semi-analytical
  model of \citet{Wise05}, updated with the 7-year WMAP parameters and
  optical depth to Thompson scattering, to calculate the LW background
  intensity, plotted in Fig. \ref{fig:uvb}.  In this semi-analytical
  model, we use a Pop III stellar mass of 100 \Ms, star formation
  efficiency of 0.005, and escape fraction of 0.2 \citep{Wise09}.  The
  LW radiation from point sources are added to the background.  The
  intensity decreases after $z \sim 14$ because Pop II star formation
  becomes dominant, which produce less LW specific luminosity than Pop
  III stars that have surface temperatures of $T = 10^5$ K.  For
  computational convenience, we fit the background evolution with the
  function
%
  \begin{equation}
    \label{eqn:uvb}
    \log_{10} J_{21}(z) = A + Bz + Cz^2 + Dz^3 + Ez^4,
  \end{equation}
%
  where $(A,B,C,D,E) = (-2.356, 0.4562, -0.02680, 5.882 \times 10^{-4},
  -5.056 \times 10^{-6})$ and $J_{21}$ is the specific intensity in
  units of $10^{-21}$ \emis.  This fits the
  model data within 1\% in $6 \le z \le 30$ and is consistent with
  $J_{21}$ values in \citet{Trenti09_SFR}.
\item Pop II star formation only.  This model is useful to study the
  importance of treating Pop III star formation as single stars and
  their pair-instability and Type II SNe.
\item Combination of metal cooling (model i) and a LW background
  (model v).  This provides the best physical scenario for the
  high-$z$ universe, and we consider it as our \textit{primary model}.
\item Combination of metal cooling (model i), increased metal yields
  (model iii), a LW background (model v).  We explain in
  \S\ref{sec:models} why we do not consider this as our primary model.
\end{enumerate}

@@

% \begin{figure}
%   \plotone{mass_fn.eps}
%   \caption{\label{fig:mass_fn} Halo DM mass function of the simulated
%     haloes (points) where the error bars are Poisson noise and the
%     solid line is the analytic halo mass function of
%     \citet{Warren06}.}
% \end{figure}

@@

Here we present the gaseous and stellar evolution of the high-redshift
dwarf galaxies that form in our \textit{primary physical model} with
metal-line radiative cooling, Pop II metal yields that agree with MW
data, and a LW radiation background.  To illustrate its global
properties, we show the density-weighted projections of gas density,
temperature, and metallicity at redshifts 15, 12, 10, 8, and 7 in
Fig. \ref{fig:evo-mosaic}.  Most apparent is the photo-heating of IGM
over this redshift range, where the mass- and volume-averaged ionized
fraction are 0.431 and 0.417 at $z=7$, respectively.  The metallicity
projections show the growth of metal-enriched bubbles, starting first
with enrichment from Pop III stars.  Then as time progresses, the
haloes enriched within these bubbles above $Z_{\rm cr}$ transition to
Pop II star formation, enriching their host halo and surrounding IGM.
Our primary model contains ?? galaxies with a total of ???? Pop II
star clusters and captures the formation of ??? Pop III stars.

% In Fig. \ref{fig:mass_fn}, we show the halo mass function, agreeing
% well with the analytic halo mass function of \citet{Warren06}.  We
% identify the haloes with a friends-of-friends (FOF) algorithm
% \citep{Davis85}.  The excess of low-mass haloes below $M_{\rm DM} = 2
% \times 10^6 \Ms$ is most likely associated with the biased region in
% the lower-right region in the projections.  Furthermore, the
% uncertainities in different analytic halo mass functions
% \citep[see][for a comparison]{Reed07} and halo identification are
% comparable than these differences.

@@

\begin{figure*}
  %\plottwo{z82-mosaic0.eps}{z82-mosaic1.eps}
  \vspace{150pt}
  \caption{\label{fig:z82-mosaic} Density-weighted projections of
    density (left), temperature (center), and metallicity (right) of
    the 10 most massive haloes at $z=8.2$ in our primary model.  The
    field of view is 5 proper kpc, and the circles have a radius of
    $r_{200}$.  The composite metallicity images are constructed in
    the same fashion as Fig. \ref{fig:evo-mosaic}.}
\end{figure*}

\begin{figure*}
  \plottwo{z10-mosaic0.eps}{z10-mosaic1.eps}
  \caption{\label{fig:z10-mosaic} Same as Fig. \ref{fig:z82-mosaic}
    but at $z=10$, showing the progenitors of the 10 most massive
    haloes at $z=8.2$.}
\end{figure*}

% \begin{figure*}
%   \plottwo{z10-mosaic0.eps}{z10-mosaic1.eps}
%   \caption{\label{fig:z10-mosaic} Same as Fig. \ref{fig:z8-mosaic} at
%     $z=10$.}
% \end{figure*}

To get a visual sense of the mass accretion and metal enrichment
history of the 10 most massive haloes, we show their density-weighted
projections of gas density, temperature, and composite Pop II+III
metallicity at redshifts 8.2 and 10 in Fig. \ref{fig:z82-mosaic} and
\ref{fig:z10-mosaic}, respectively.  One common feature of all of the
halos represented in these Figures is that they are embedded in a
preheated IGM with the exception of Halo 7 at $z=10$.  Prior radiative
feedback in either the host or nearby halos created \hii~regions that
encompass these halos.  For \hii~regions without sustained star
formation, these so-called relic \hii~regions recombine and
radiatively cool down to $T = 10^3$ K.  Within the virial radius, one
can see that our simulations capture the multi-phase ISM.  In the
density projections, the effects of photo-evaporation and cloud
crushing are clearly seen, which are caused by the stellar radiative
and mechanical feedback, respectively.  The filaments adjacent to the
halos are photo-heated to $T = 1-3 \times 10^4$ K, and then their gas
escapes into the IGM no longer being pressure equilibrium with the
gravitational potential of the filament, i.e. Jeans smoothing.
Furthermore, neighboring halos are photo-evaporated \citep[see][for
the level of halo photo-evaporation]{Wise08_Reion}, resulting in the
suppression of gas-rich satellite haloes.  A good illustration of
photo-evaporation in progress is the cometary structure in the
bottom-center of the density projection of Halo 4 at $z=7$.

@@

\section{Variations between Physical Models}
\label{sec:models}

\subsection{Reference Model}

@@
